### 2025-10-28 Text/Thesis/Chapters/Chapter3.qmd
Fix: corrected table layout

\renewcommand{\arraystretch}{1.8} 
```{r}
#| label: tbl-out-shannon
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.'
#| tbl-pos: 'htb'

@@

# Generar tabla con kable (latex)
knitr::kable(
  combined_results,
#  caption    = "Processing time for bootstrap-improved estimators \\(\\widetilde{H}_{\\text{C}}\\) and \\(\\widetilde{H}_{\\text{AO}}\\).",
  format     = "latex",
  booktabs   = TRUE,
  align      = "cccc",
  escape     = FALSE,
  #label      = "table_time",
  #table.envir= "table",
 # position   = "htb",
  linesep    = ""
) %>%
  row_spec(4,  extra_latex_after = "\\cline{3-4}") %>%
  row_spec(12, extra_latex_after = "\\cline{3-4}") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(font_size = 10,latex_options = "scale_down", full_width = TRUE)
```
\vspace{-20pt}

@@

The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures. These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

As expected, power increased with both the sample size and the number of looks. This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

\renewcommand{\arraystretch}{0.9}
```{r Table_size_and_power-shannon3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
suppressMessages({
  suppressWarnings({
    load("./Data/type_I_results-shannon.Rdata")
    type_I_error_rates <- tapply(
      results$P_Value, 
      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
      FUN = function(p_values) sum(p_values) / length(p_values)
    )

@@

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{H}}(\\bm{Z})$ test statistic (Shannon).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power_shannon",
  centering = FALSE,
  table.envir = "table", 
  position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3, "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10) %>%
  kable_styling(full_width = T)

@@

\renewcommand{\arraystretch}{0.9}
```{r Table_size_and_power-renyi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
suppressMessages({
  suppressWarnings({

@@

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z})$ test statistic (Rényi).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  label = "size-power-renyi",
  centering = FALSE,
  table.envir = "table", 
  position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10) %>%
  kable_styling(full_width = T)

@@

\renewcommand{\arraystretch}{1}
```{r Table_size_and_power-tsallis0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
suppressMessages({
  suppressWarnings({

@@

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  label = "size-power-tsallis",
  centering = FALSE,
  table.envir = "table", 
  position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10) %>%
  kable_styling(full_width = T)

@@

```{r fig-compare_size_power_plot0,  eval=FALSE,  include=FALSE, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies. Size and Power for different sample sizes and $L$ values."}
library(ggplot2)

>>>>

\renewcommand{\arraystretch}{1.8} 
```{r}
#| label: tbl-out-shannon
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$'
#| tbl-pos: 'htb'

@@

# Generar tabla con kable (latex)
knitr::kable(
  combined_results,
#  caption    = "Processing time for bootstrap-improved estimators \\(\\widetilde{H}_{\\text{C}}\\) and \\(\\widetilde{H}_{\\text{AO}}\\).",
  format     = "latex",
  booktabs   = TRUE,
  align      = "cccc",
  escape     = FALSE,
  #label      = "table_time",
  #table.envir= "table",
 # position   = "htb",
  linesep    = ""
) %>%
  row_spec(4,  extra_latex_after = "\\cline{3-4}") %>%
  row_spec(12, extra_latex_after = "\\cline{3-4}") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(font_size = 10,latex_options = "scale_down")%>%
 column_spec(1, width = "3.5cm") %>%
column_spec(2, width = "3.5cm") %>%
column_spec(3, width = "3.5cm") %>%
column_spec(4, width = "3.5cm")

```
\vspace{-20pt}

@@

The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures. These results are summarized in Tables&nbsp;[-@tbl-table_size_power_shannon]--[-@tbl-size-power-tsallis], and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

As expected, power increased with both the sample size and the number of looks. This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
The results are shown in Tables&nbsp;[-@tbl-table_size_power_shannon]--[-@tbl-size-power-tsallis], with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.

@@

\renewcommand{\arraystretch}{0.9}
```{r}
#| label: tbl-table_size_power_shannon
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Size and Power of the $S_{\widetilde{H}}(\bm{Z})$ test statistic (Shannon)'
#| tbl-pos: 'H'
suppressMessages({
  suppressWarnings({
    load("./Data/type_I_results-shannon.Rdata")
    type_I_error_rates <- tapply(
      results$P_Value, 
      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
      FUN = function(p_values) sum(p_values) / length(p_values)
    )

@@

table_combined_result <- knitr::kable(
  combined_results,
 # caption = "Size and Power of the $S_{\\widetilde{H}}(\\bm{Z})$ test statistic (Shannon).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  #label = "table_size_power_shannon",
  centering = FALSE,
  #table.envir = "table", 
  #position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3, "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10)%>%
  column_spec(1, width = "1.5cm") %>%
  column_spec(2, width = "1.5cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "1.5cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "1.5cm") %>%
  column_spec(7, width = "1.5cm") %>%
  column_spec(8, width = "1.5cm")
  #kable_styling(full_width = T)

@@

\renewcommand{\arraystretch}{0.9}
```{r}
#| label: tbl-size-power-renyi
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Size and Power of the $S_{\widetilde{R}_{\lambda}}(\bm{Z})$ test statistic (Rényi)'
#| tbl-pos: 'H'
suppressMessages({
  suppressWarnings({

@@

table_combined_result <- knitr::kable(
  combined_results,
  #caption = "Size and Power of the $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z})$ test statistic (Rényi).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  #label = "size-power-renyi",
  centering = FALSE,
  #table.envir = "table", 
  #position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10)%>%
  column_spec(1, width = "1.5cm") %>%
  column_spec(2, width = "1.5cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "1.5cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "1.5cm") %>%
  column_spec(7, width = "1.5cm") %>%
  column_spec(8, width = "1.5cm")
  #kable_styling(full_width = T)

@@

\renewcommand{\arraystretch}{1}
```{r}
#| label: tbl-size-power-tsallis
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis)'
#| tbl-pos: 'H'
suppressMessages({
  suppressWarnings({

@@

table_combined_result <- knitr::kable(
  combined_results,
  #caption = "Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis).",
  format = "latex",
  booktabs = TRUE,
  align = "cccccccc",
  escape = FALSE,
  digits = 3,
  #label = "size-power-tsallis",
  centering = FALSE,
  #table.envir = "table", 
  #position="H", 
  linesep = ""
) %>%
  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 10)%>%
  column_spec(1, width = "1.5cm") %>%
  column_spec(2, width = "1.5cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "1.5cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "1.5cm") %>%
  column_spec(7, width = "1.5cm") %>%
  column_spec(8, width = "1.5cm")

  #kable_styling(full_width = T)

@@

```{r fig-compare_size_power_plot0,  eval=FALSE,  include=FALSE, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies. Size and Power for different sample sizes and $L$ values."}

### 2025-10-28 Text/Thesis/Chapters/Chapter4.qmd
Fix: corrected table layout

The SAR images come from TanDEM-X (X-band), UAVSAR (L-band), and Sentinel-1B (C-band). The two UAVSAR images were obtained from the Alaska Satellite Facility (ASF)\footnote{\url{https://search.asf.alaska.edu/}}, which provides airborne and satellite SAR data. The X-band images were downloaded from ESA’s Third Party Missions (ESA TPM)\footnote{\url{https://tpm-ds.eo.esa.int/collections/}}, and the C-band image from Copernicus Data Space. All images use single polarization (HH or VV), and their acquisition settings differ in resolution, scene size, and number of looks. Table&nbsp;\ref{tab:table_param} lists the main characteristics of each SAR image.

\renewcommand{\arraystretch}{2}   
```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}

SAR_data <- data.frame(
  Site = c("London",  "Munich","New Orleans", "Dublin","Coast of Jalisco" ),
  Mission = c("TanDEM-X", "UAVSAR", "UAVSAR", "TanDEM-X", "Sentinel-1B"),
  Band = c("X", "L","L", "X", "C"),
  Polarization = c("HH", "HH","HH","HH", "VV"),
  Size = c("$2000\\times2000$",  "$1024\\times1024$","$1400\\times1400$", "$1100\\times1100$","$512\\times512$"),
  L = c(1,  12, 12,  16,18),
  Resol = c("$0.99/0.99$",  "$4.9/7.2$","$4.9/7.2$", "$1.35/1.35$","$40/40$"),
  Date = c("12-11-2021", "16-04-2015","13-03-2016", "03-09-2017","29-08-2021")
)

@@

kable(SAR_data, 
      format = "latex",
      booktabs = TRUE,
      align = "cccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = TRUE,
      caption = "Parameters of selected SAR images.",
      table.envir = "table", position = "hbt") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 21) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.8cm") %>%
  column_spec(2, width = "3.7cm") %>%
  column_spec(3, width = "2.5cm") %>%
  column_spec(4, width = "3.5cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, width = "4.0cm") %>%
  column_spec(8, width = "4.5cm")

@@

In addition to the visual analysis presented above, we measured execution times to assess the computational cost of the proposed methods. Table&nbsp;\ref{tab:table_exec_times} reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$). Times are reported in minutes and seconds (mm:ss) with $B=100$ bootstrap replications per window.

@@

\renewcommand{\arraystretch}{1.8}   
```{r times_sar_images2, echo=FALSE, message=FALSE, warning=FALSE}

@@

kable(Times_data,
format = "latex",
booktabs = TRUE,
align = "ccccc",
escape = FALSE,
label = "table_exec_times",#adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$)
centering = TRUE,
caption = "Execution times for the heterogeneity detection using fixed $7\\times7$ and adaptive windows ($N_{\\min}=5$, $N_{\\max}=11$), with $B=100$ bootstrap replications per scenario. Times are given in minutes and seconds (mm:ss). Rényi entropy uses $\\lambda=0.9$ and Tsallis entropy uses $\\lambda=0.85$.",
table.envir = "table", position = "hbt") %>%
row_spec(0, align = "c") %>%
kable_styling(latex_options = "scale_down", font_size = 16) %>%
kable_styling(full_width = TRUE) %>%
column_spec(1, width = "5cm") %>%
column_spec(2, width = "3.5cm") %>%
column_spec(3, width = "3.5cm") %>%
column_spec(4, width = "3.5cm") %>%
column_spec(5, width = "4cm")

@@

All experiments were executed on the workstation described in @sec-repr, using 8–16 CPU cores. 
This setup allowed the entropy-based heterogeneity detection tests to process medium-sized SAR scenes within a few minutes, as reported in Table&nbsp;\ref{tab:table_exec_times}.

@@

Eight polygonal regions of interest (ROIs) were manually selected for each of the three SAR scenes used in the quantitative study—London, Munich, and Dublin (Figures&nbsp;\ref{fig:london-sar-roi1}–\ref{fig:dublin-sar-roi1}). ROIs labeled in red correspond to heterogeneous areas (class 1) and those in blue to homogeneous areas (class 0). The polygons were rasterized to the image grid to form a partial ground truth. We thresholded the $p$-value maps at $\alpha=0.05$, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared the resulting decisions with the ground truth to compute the F1-score ($F_1$), the Kappa coefficient ($\kappa$), and the overall accuracy (OA). Results are summarized in Table&nbsp;\ref{tab:table_metrics1}.

@@

\renewcommand{\arraystretch}{1.3}
```{r metrics_table_k, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
suppressPackageStartupMessages({
library(dplyr)
library(knitr)
library(kableExtra)
})

@@

kable(all_metrics,
caption = "Quantitative measures of heterogeneity detection",
format = "latex",
booktabs = TRUE,
align = "ccccc",      
escape = FALSE,
label = "table_metrics1",
row.names = FALSE) %>%
row_spec(0, align = "c") %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "bottom") %>%
kable_styling(latex_options = c("hold_position","scale_down"), font_size = 11, full_width = T) %>%
print()

>>>>

The SAR images come from TanDEM-X (X-band), UAVSAR (L-band), and Sentinel-1B (C-band). The two UAVSAR images were obtained from the Alaska Satellite Facility (ASF)\footnote{\url{https://search.asf.alaska.edu/}}, which provides airborne and satellite SAR data. The X-band images were downloaded from ESA’s Third Party Missions (ESA TPM)\footnote{\url{https://tpm-ds.eo.esa.int/collections/}}, and the C-band image from Copernicus Data Space. All images use single polarization (HH or VV), and their acquisition settings differ in resolution, scene size, and number of looks. @tbl-table_param lists the main characteristics of each SAR image.

\renewcommand{\arraystretch}{1}   
```{r}
#| label: tbl-table_param
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Parameters of selected SAR images'
#| tbl-pos: 'H'
#| 
SAR_data <- data.frame(
  Site = c("London",  "Munich","New Orleans", "Dublin","Coast of Jalisco" ),
  Mission = c("TanDEM-X", "UAVSAR", "UAVSAR", "TanDEM-X", "Sentinel-1B"),
  Band = c("X", "L","L", "X", "C"),
  Polarization = c("HH", "HH","HH","HH", "VV"),
  Size = c("$2000\\times2000$",  "$1024\\times1024$","$1400\\times1400$", "$1100\\times1100$","$512\\times512$"),
  L = c(1,  12, 12,  16,18),
  Resol = c("$0.99/0.99$",  "$4.9/7.2$","$4.9/7.2$", "$1.35/1.35$","$40/40$"),
  Date = c("12-11-2021", "16-04-2015","13-03-2016", "03-09-2017","29-08-2021")
)

@@

kable(SAR_data, 
      format = "latex",
      booktabs = TRUE,
      align = "cccccccc",
      escape = FALSE,
      digits = 2,
      #label = "table_param",
      centering = TRUE
     # caption = "Parameters of selected SAR images.",
     # table.envir = "table", position = "hbt"
      ) %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 21) %>% 
  #kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.8cm") %>%
  column_spec(2, width = "3.7cm") %>%
  column_spec(3, width = "2.5cm") %>%
  column_spec(4, width = "3.5cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, width = "4.0cm") %>%
  column_spec(8, width = "4.5cm")

@@

In addition to the visual analysis presented above, we measured execution times to assess the computational cost of the proposed methods. @tbl-exec-times reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$). Times are reported in minutes and seconds (mm:ss) with $B=100$ bootstrap replications per window.

@@

\renewcommand{\arraystretch}{1.8} 
```{r}
#| label: tbl-exec-times
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Execution times for the heterogeneity detection using fixed $7\times7$ and adaptive windows ($N_{\min}=5$, $N_{\max}=11$), with $B=100$ bootstrap replications per scenario. Times are given in minutes and seconds (mm:ss). Rényi entropy uses $\lambda=0.9$ and Tsallis entropy uses $\lambda=0.85$'
#| tbl-pos: 'hbt'

@@

kable(Times_data,
format = "latex",
booktabs = TRUE,
align = "ccccc",
escape = FALSE,
#label = "table_exec_times",#adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$)
centering = TRUE
#caption = "Execution times for the heterogeneity detection using fixed $7\\times7$ and adaptive windows ($N_{\\min}=5$, $N_{\\max}=11$), with $B=100$ bootstrap replications per scenario. Times are given in minutes and seconds (mm:ss). Rényi entropy uses $\\lambda=0.9$ and Tsallis entropy uses $\\lambda=0.85$.",
#table.envir = "table", position = "hbt"
) %>%
row_spec(0, align = "c") %>%
kable_styling(latex_options = "scale_down", font_size = 14) %>%
#kable_styling(full_width = TRUE) %>%
column_spec(1, width = "5cm") %>%
column_spec(2, width = "3.5cm") %>%
column_spec(3, width = "3.5cm") %>%
column_spec(4, width = "3.5cm") %>%
column_spec(5, width = "4cm")

@@

All experiments were executed on the workstation described in @sec-repr, using 8–16 CPU cores. 
This setup allowed the entropy-based heterogeneity detection tests to process medium-sized SAR scenes within a few minutes, as reported in @tbl-exec-times.

@@

Eight polygonal regions of interest (ROIs) were manually selected for each of the three SAR scenes used in the quantitative study—London, Munich, and Dublin (Figures&nbsp;\ref{fig:london-sar-roi1}–\ref{fig:dublin-sar-roi1}). ROIs labeled in red correspond to heterogeneous areas (class 1) and those in blue to homogeneous areas (class 0). The polygons were rasterized to the image grid to form a partial ground truth. We thresholded the $p$-value maps at $\alpha=0.05$, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared the resulting decisions with the ground truth to compute the F1-score ($F_1$), the Kappa coefficient ($\kappa$), and the overall accuracy (OA). Results are summarized in @tbl-table-metrics1.

@@

\renewcommand{\arraystretch}{1.3}
```{r}
#| label: tbl-table-metrics1
#| echo: false
#| message: false
#| warning: false
#| results: 'asis'
#| tbl-cap: 'Quantitative measures of heterogeneity detection'
#| tbl-pos: 'htb'
suppressPackageStartupMessages({
library(dplyr)
library(knitr)
library(kableExtra)
})

@@

kable(all_metrics,
#caption = "Quantitative measures of heterogeneity detection",
format = "latex",
booktabs = TRUE,
align = "ccccc",      
escape = FALSE,
#label = "table_metrics1",
row.names = FALSE) %>%
row_spec(0, align = "c") %>%
collapse_rows(columns = 1, latex_hline = "major", valign = "bottom") %>%
kable_styling(latex_options = c("hold_position","scale_down"), font_size = 14) %>%
column_spec(1, width = "5cm") %>%
column_spec(2, width = "3.5cm") %>%
column_spec(3, width = "3.5cm") %>%
column_spec(4, width = "3.5cm") %>%
column_spec(5, width = "4cm")%>%
#kable_styling(latex_options = c("hold_position","scale_down"), font_size = 11, full_width = T)
print()
